Robust Winner Determination and Simultaneous Elicitation of Scoring Rules and Preferences

### 2018-12-05 draft.tex
small changes

\begin{itemize}
 \item Case of convex sequences:
  %{\em Explain why convex sequences do not pose any problem}
In the case of convex sequences, the optimization can be done without integer variables, since the case $A^-$ can be easily dealt with, and alternatives in $U$ can be indifferently be placed either to the top or to the bottom.
\begin{align*}
\max_{\w} & \sum_{j=1}^{n}  [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \\
\text{s.t.} & \w \in W
\end{align*}
The space of feasible weights $W$ is encoded with linear constraints.
Therefore the pairwise maximum regret can be computed with a linear program.

@@

\begin{itemize}
\item Current solution strategy:
%Assume $x$ is the minimax regret optimal alternative $y$ the adversarial choice

\item Non-iterleaved regret method:

>>>>

\begin{itemize}
 \item Case of convex sequences:
  %{\em Explain why convex sequences do not pose any problem}
In the case of convex sequences, the optimization can be done without integer variables, since the case $A^-$ can be easily dealt with, and alternatives in $U$ can be indifferently be placed either to the top or to the bottom.
\begin{align*}
\max_{\w} & \sum_{j=1}^{n}  [w_{\hat{v}_j(y)} - w_{\hat{v}_j(x)}] \\
\text{s.t.} & \w \in W
\end{align*}
The space of feasible weights $W$ is encoded with linear constraints that model the preferences of the committee.
Therefore the pairwise maximum regret can be computed with a linear program.

@@

\begin{itemize}
\item Current solution strategy: consider the solution of the minimax regret game, 
 $(x,y,w^{a},\profile^{a})$, where $x$ is the minimax regret optimal alternative, $y$ the adversarial choice, $w^{a}$ the weights, and $\profile^{a}$ the profile completed by the adversary.

\item Non-iterleaved regret method: comparison with a method based on minimax regret, but not interleaved.
